---
title: "Daily Schedule"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<button class="accordion">Before Starting the Program</button>
<div class="panel">  

| To-Do         |                              | 
|---------------|------------------------------------|
| Download and Install R | [Link](https://mirror.las.iastate.edu/CRAN/) [Video](https://uci.yuja.com/V/Video?v=3173351&node=10757512&a=280036139&autoplay=1) |
| Download and Install RStudio| [Link](https://www.rstudio.com/products/rstudio/download/)  [Video](https://uci.yuja.com/V/Video?v=3173359&node=10757552&a=664679852&autoplay=1)     |
|Setup RStudio| [Video](https://uci.yuja.com/V/Video?v=3173384&node=10757676&a=717681262&autoplay=1)       |
|Download packages |<a href="R-code/code-00-setup.R" download>File</a> [Video](https://uci.yuja.com/V/Video?v=3173415&node=10757778&a=1269482034&autoplay=1)     |


</div>
		
<!-- connecting to UCI email address-->
		
<button class="accordion">Day 1 &#9679; July 6 &#9679; Introduction to COSMOS, R, and Data</button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 09:30 | Welcome                            |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/01a-welcome.html)       |
| 09:35 - 10:30 | Introduction to R and R Markdown   |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/01b-intro-r.html)       |
| 10:45 - 12:00 | Introduction to Data               |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/01c-intro-data.html) &#9679; [File](https://cosmos-uci-dshs.github.io/dshs-starter-codes/week01/01c-intro-data.Rmd)     |

</div>
		

<button class="accordion">Day 2 &#9679; July 7 &#9679; Summarizing Data </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 09:50 | Describing Data with Numbers                            |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/02a-describe-data.html) &#9679; [File](https://cosmos-uci-dshs.github.io/dshs-starter-codes/week01/02a-describe-data.Rmd)|
| 10:00 - 10:50 | Interpeting Data Visualizations   |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/02b-interpret-dataviz.html)       |
| 11:00 - 12:00 | Visualizing Data               |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/02c-visualize-data.html) &#9679; [File](https://cosmos-uci-dshs.github.io/dshs-starter-codes/week01/02c-visualize-data.Rmd)     |
| 13:00 - 15:00 | Lab: Summarizing Data               | [File](https://cosmos-uci-dshs.github.io/dshs-starter-codes/week01/02d-lab-summarize-data.Rmd)     |

</div>
		
<button class="accordion">Day 3 &#9679; July 8 &#9679; Data Wrangling</button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 09:40 | Improving Data Visualizations                            |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/03a-improve-dataviz.html) &#9679; [File](https://cosmos-uci-dshs.github.io/dshs-starter-codes/week01/03a-improve-dataviz.Rmd)|
| 09:40 - 10:00 | Pipe operator   |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/03b-pipe-op.html)       |
| 10:10 - 11:00 | Subsetting and Grouping Data               |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/03c-subset-group.html) &#9679; [File](https://cosmos-uci-dshs.github.io/dshs-starter-codes/week01/03c-data-wrangle.Rmd)     |
| 11:10 - 12:00 | Changing Variables              |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/03d-change-variable.html)    |

</div>
		
<button class="accordion">Day 4 &#9679; July 9 &#9679; Dealing with Data Frames</button>
<div class="panel"> 

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 09:30 | R packages                            |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/04a-R-packages.html) &#9679; [File](https://cosmos-uci-dshs.github.io/dshs-starter-codes/week01/04a-R-packages.Rmd)|
| 09:30 - 10:00 | Importing Data   |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/04b-import-data.html)       |
| 10:10 - 11:00 | Data Joins               |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/04c-join-data.html) &#9679; [File](https://cosmos-uci-dshs.github.io/dshs-starter-codes/week01/04c-data-joins.Rmd)     |
| 11:10 - 12:00 | Review              |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week01/04d-review.html)  &#9679; [File](https://cosmos-uci-dshs.github.io/dshs-starter-codes/week01/04d-review.Rmd)   |
| 13:00 - 15:00 | Lab: Exploring Data              |[Activity](https://cosmos-uci-dshs.github.io/dshs-starter-codes/week01/04e-explore-data.html){target="_blank"}    |

</div>
		
<button class="accordion">Day 5 &#9679; July 12 &#9679; Probability</button>
<div class="panel"> 

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 09:50 | Introduction to probability                           |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week02/05a-intro-prob.html) &#9679;  [Activity](https://cosmos-uci-dshs.github.io/dshs-starter-codes/week02/05b-prob-activity.html){target="_blank"}|
| 10:00 - 10:50 | Joint vs. marginal   | |
| 11:00 - 12:00 | Conditional probability and independence | |

</div>
		
<button class="accordion">Day 6 &#9679; July 13 &#9679; Random variables</button>
<div class="panel"> 


| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 09:50 | Random variables             |[Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week02/06-a-random-variables.html) &#9679; |
| 10:00 - 10:50 | Probability distributions   | |
| 11:00 - 12:00 | Discrete vs. continuous distributions | |


</div>
		
<button class="accordion">Day 7 &#9679; July 14 &#9679; Estimation</button>
<div class="panel"> 

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 09:50 | Point vs. interval estimates      | |
| 10:00 - 10:50 | Sampling distribution    | |
| 11:00 - 12:00 | Confidence internval | |

</div>
		
<button class="accordion">Day 8 &#9679; July 15 &#9679; Hypothesis testing</button>
<div class="panel"> 

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 09:50 | Null vs. alternative      | [Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week02/08-a-hypothesis.html) &#9679;|
| 10:00 - 10:50 | t-test    | |
| 11:00 - 12:00 | Chi-squared test | |

</div>
		
<button class="accordion">Day 9 &#9679; July 16 &#9679; Testing relationships</button>
<div class="panel">


| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 09:50 | Two-sample t-test      | [Slides](https://cosmos-uci-dshs.github.io/dshs-slides/week02/09-a-relationship.html) &#9679; |
| 10:00 - 10:50 | Chi-squared test for contingency tables    | |
| 11:00 - 12:00 | Nonparametric tests | |

</div>
		
<button class="accordion">Day 10 &#9679; July 19</button>
<div class="panel"> 


Under Construction

</div>
		
<button class="accordion">Day 11 &#9679; July 20</button>
<div class="panel"> 


Under Construction

</div>
		
<button class="accordion">Day 12 &#9679; July 21</button>
<div class="panel"> 

Under Construction

</div>
		
<button class="accordion">Day 13 &#9679; July 22</button>
<div class="panel"> 

Under Construction

</div>

<button class="accordion">Day 14 &#9679; July 23</button>
<div class="panel"> 

Under Construction

</div>

<button class="accordion">Day 15 &#9679; July 26</button>
<div class="panel"> 

Under Construction

</div>

<button class="accordion">Day 16 &#9679; July 27</button>
<div class="panel"> 


Under Construction

</div>

<button class="accordion">Day 17 &#9679; July 28</button>
<div class="panel"> 

Under Construction

</div>
		
<button class="accordion">Day 18 &#9679; July 29</button>
<div class="panel"> 

Under Construction

</div>
		
<button class="accordion">Day 19 &#9679; July 30</button>

<div class="panel">

Under Construction

</div>
		
<button class="accordion">Day 20 &#9679; July 31</button>
<div class="panel"> <


Under Construction

</div>

```{r}
htmltools::tagList(
  htmltools::tags$script(src = "https://d3js.org/d3.v4.min.js"),
  htmltools::tags$script(src = "https://cdnjs.cloudflare.com/ajax/libs/dimple/2.3.0/dimple.latest.min.js")
)
```

```{js, class.source = "jsvis1"}
var acc = document.getElementsByClassName("accordion");
var i;

for (i = 0; i < acc.length; i++) {
  acc[i].addEventListener("click", function() {
    /* Toggle between adding and removing the "active" class,
    to highlight the button that controls the panel */
    this.classList.toggle("active");

    /* Toggle between hiding and showing the active panel */
    var panel = this.nextElementSibling;
    if (panel.style.display === "block") {
      panel.style.display = "none";
    } else {
      panel.style.display = "block";
    }
  });
}
```
